### 2020-02-13 README.Rmd
Tweaking BigWoods CV grid
Cleaned up spatial CV

@@

```{r}
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, k = 28, yOffset = 0.6, verbose = FALSE
)

@@

Using the [`blockCV`](https://github.com/rvalavi/blockCV) package, in particular the example code in the package [vignette](http://htmlpreview.github.io/?https://github.com/rvalavi/blockCV/blob/master/vignettes/BlockCV_for_SDM.html), we

* Define the blocking structure
* Determine the degree of spatial autocorrelation for various `max_dist` values
* If the above doesn't work, the go back to what we used for PLOS paper.

>>>>

We use the [`blockCV`](https://github.com/rvalavi/blockCV) package to define the spatial grid, whose elements will act as the folds in our leave-one-out (by "one" we meen "one grid block") cross-validation scheme.

@@

```{r}
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, k = 28, 
  xOffset = 0.5, yOffset = 0.99999,
  verbose = FALSE
)

@@
